\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2015-03-03 Report/project_report.tex
Removed rotational rmse from KITTI

\begin{figure*}
    \centering
    \subfigure[RMSE on KITTI traverse \texttt{0001}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_2011_09_26_drive_0001}
    }
    ~
    \subfigure[RMSE on KITTI traverse \texttt{0036}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_2011_09_26_drive_0036}
    }

    \subfigure[RMSE on KITTI traverse \texttt{0051}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_2011_09_26_drive_0051}
    }
    ~
    \subfigure[RMSE on KITTI traverse \texttt{0095}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_2011_09_26_drive_0095}
    }
    \caption{Translational and rotational RMSE over four traverses from the KITTI dataset \cite{Geiger:2013:IJRR} totaling 534 m of urban driving.}
    \label{fig:kitti}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \subfigure[RMSE on KITTI traverse \texttt{0001}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_trans_2011_09_26_drive_0001}
    }
    ~
    \subfigure[RMSE on KITTI traverse \texttt{0036}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_trans_2011_09_26_drive_0036}
    }

    \subfigure[RMSE on KITTI traverse \texttt{0051}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_trans_2011_09_26_drive_0051}
    }
    ~
    \subfigure[RMSE on KITTI traverse \texttt{0095}.] {
        \centering
        \includegraphics[width=0.45\textwidth]{figs/kitti/RMSE_trans_2011_09_26_drive_0095}
    }
    \caption{Translational and rotational RMSE over four traverses from the KITTI dataset \cite{Geiger:2013:IJRR} totaling 534 m of urban driving.}
    \label{fig:kitti}
\end{figure*}
